---
title: "Load Packages"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Load Packages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## util_pkgload

The `util_pkgload` function
checks if packages in character vector are installed,
installs them if they are not currently installed,
and loads them.

## Use case

Typically,
packages are installed and loaded using the following code.
Installing and loading libraries this way can be tedious
especially when the list of packages to install is long.
The package are also re-installed
even if they are already installed in the system.
This takes time.

```{r, eval=FALSE}
packages <- c(
  "testthat",
  "devtools",
  "rmarkdown"
)
install.packages(packages)
library("testthat")
library("devtools")
library("rmarkdown")
```

The above task is executed with a single call below.
The function does more.
**If the packages are already installed,
the installation process is skipped.
This is a great time saver.**
All the packages in vector are loaded in the namespace.

```{r, eval=FALSE}
library(jeksterslabRutils)
util_pkgload(packages)
```

